A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-09-12 04_Severity_MetaAnalysis.Rmd
Revise header to match other chapter title capitalisation

```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvSQ <- rma.mv(
   yi = yi_square,
   V = vi_square,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

>>>>

```{r Metafor-Sev-analysisSQ, cache=TRUE}
PMsev_mvSQ <- rma.mv(
   yi = yi_square,
   V = vi_square,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)
